\\textsc{Mathematical Description}

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Write size data likelihood assumptions text

@@

type_key = c(
  "abund" = "Abundance",
  "surv" = "Survival",
  "comp" = "Composition"
)

>>>>

### Mean Length Data Sources

Upon capture for PIT tagging, individual fish lengths are measured.
We calculated the mean length (and the associated standard errors) of all captured fish (tagged and untagged; only fish $\ge$ 55mm can receive a PIT tag) and used them in log-normal likelihoods by assuming:

\begin{equation}
\log\left(\hat{L}^{P^{b}}_{y,j}\right) \sim \Ndist\left[\log\left(L^{P^{b}}_{y,j}\right), \hat{\sigma}_{L^{P^{b}}_{y,j}}\right]
(\#eq:L-Pb-data)
\end{equation}

for mean length data for the summer parr tagging group and

\begin{equation}
\log\left(\hat{L}^{M^{b}}_{y,j}\right) \sim \Ndist\left[\log\left(L^{M^{b}}_{y,j}\right), \hat{\sigma}_{L^{M^{b}}_{y,j}}\right]
(\#eq:L-Mb-data)
\end{equation}

for mean length data for the smolt tagging group.
Because the each population has approximately 1,000 fish tagged and measured during each tagging event, the standard errors on the mean length estimates were quite small.

@@

type_key = c(
  "abund" = "Abundance",
  "surv" = "Survival",
  "length" = "Length",
  "comp" = "Composition"
)
